EoS-insensitive relations after GW170817

### 2019-02-09 paper/bin-love-after-gw170817.tex
removed BL hybrid star section and discussed why it didnt work and how well improve on it in future works

\subsection{Binary love relations}\label{sec:binary}
Next we consider improvements to the binary Love relations.
Similar to Sec.~\ref{sec:ilq}, we consider two classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
We begin in Sec.~\ref{sec:binLove-nuclear} by fitting new binary Love relations to the nucleonic matter EoSs as was done in~\cite{Yagi:binLove}.
This is followed in Sec.~\ref{sec:binLove-hybrid} by an analysis and discussion into different fits which incorporate hybrid star EoSs.

\subsubsection{Nuclear matter stars}\label{sec:binLove-nuclear}
Following Ref.~\cite{Yagi:binLove}, we fit the binary Love relations to the constrained and unconstrained EoSs using the two-dimensional curve:
\begin{equation}\label{eq:binLovefit}
\Lambda_a=F_n(q) \frac{1+ \sum_{i=1}^3 \sum_{j=1}^2 b_{ij}q^j x^{i/5}}{1 + \sum_{i=1}^3 \sum_{j=1}^2 c_{ij}q^j x^{i/5}} \Lambda_s^{\alpha}.
\end{equation}
Here, q is the mass ratio $q \equiv m_1/m_2$ with $m_1 \leq m_2$, and $F_n(q)$ is the Newtonian-limiting control factor given by:
\begin{equation}
F_n(q) \equiv \frac{1-q^{10/(3-n)}}{1+q^{10/(3-n)}}.
\end{equation}
The updated fit parameters for the constrained set of EoSs can be found in Table~\ref{tab:binLovefit}.
Notice how, unlike the individual NS I-Love-Q relations, these relations also depend on the ratio of constituent masses in the binary system.
\begin{table*}
\centering
\caption{
Updated fit parameters for the binary Love relations, as given by the curve found in Eq.~\ref{eq:binLovefit}.
The bottom row corresponds to separate fits corresponding to the hybrid star branch of the hybrid EoSs.
}\label{tab:binLovefit}
\addtolength{\tabcolsep}{1pt} 
\begin{tabular}{c | c  c  c  c  c  c  c  c c c c c c c} 
 \hline
 \hline
 Fit & $n$ & $\alpha$ & $b_{11}$ & $b_{12}$ & $b_{21}$ & $b_{22}$ & $b_{31}$ & $b_{32}$ & $c_{11}$ & $c_{12}$ & $c_{21}$ & $c_{22}$ & $c_{31}$ & $c_{32}$\\
 \hline
 NS & $0.743$ & $-1$ & $-14.40$ & $14.45$ & $31.36$ & $-32.25$ & $-22.44$ & $20.35$ & $-15.25$ & $15.37$ & $37.33$ & $-43.20$ & $-29.93$ & $35.18$\\
 HS & $0.743$ & $-1$ & $343.0$ & $-382.6$ & $519.5$ & $-594.3$ & $811.6$ & $-867.6$ & $82.60$ & $-97.79$ & $242.2$ & $-262.9$ & $244.9$ & $-268.8$\\
 \hline
 \hline
\end{tabular}
\addtolength{\tabcolsep}{-1pt}
\end{table*}

Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both the constrained and unconstrained sets of EoSs.
Observe how once again, the constrained set of EoSs show a considerable improvement upon both the unconstrained set of EoSs, as well as the results found in previous works~\cite{Yagi:binLove}.
Additionally, the unconstrained set of EoSs show similar, yet slightly larger EoS variation than was previously found in Ref.~\cite{Yagi:binLove} due to the random sampling taken into account in this analysis.
Once again, the maximum EoS variability (in terms of fractional difference from the fit for comparison purposes) is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio.

\begin{figure}
\begin{center} 
\includegraphics[width=\linewidth]{binLoveAbsolute.eps}%{binLove.eps}
\end{center}
\caption{
Binary Love relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
In this figure, the top panel displays the EoS-insensitive relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines (note there are 2 fits for each mass ratio, corresponding to the constrained and unconstrained sets of EoSs), while the bottom 3 panels correspond to the absolute EoS variation for each mass ratio.
Observe how the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
The maximal EoS variability (shown as a the fractional difference for comparison purposes) for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
Additionally shown is the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves), as well as the HS fits (dot-dashed blue curves) discussed in Sec.~\ref{sec:binLove-hybrid}.
Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
This is shown in the bottom three panels as the absolute difference from the NS fit for comparison, while the HS fits show similar EoS variability to the constrained EoSs.
}
\label{fig:binLove}
\end{figure}

\subsubsection{Hybrid quark-hadron stars}\label{sec:binLove-hybrid}
As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
We consider 3 classes of binary systems in this analysis:
\begin{itemize}
\item HS/NS binary: consists of one massive hybrid star, and one small hadronic neutron star,
\item NS/NS binary: consists of two small-mass hadronic neutron stars,
\item HS/HS binary: consists of two massive hybrid stars.
\end{itemize}

To determine how each of class of binary NS systems obey our improved binary Love relations, we pick a representative set of 10 binary pairs from each class from the ACB5 hybrid EoS, with a transition at $M_{\text{tr}} \approx 1.4 \text{ M}_{\odot}$.
Binary Love values are computed for each pair, and fractional residuals from the binary Love curve found in Sec.~\ref{sec:binLove-nuclear} are determined and compared to the values from the constrained set of EoSs.
The results are shown in Fig.~\ref{fig:hybrid}.
First, we note that the NS/NS combination of stars gives consistent results to that found earlier -- as expected.
Next, we observe that HS/HS combinations agree moderately with previous relations\footnote{Note that these EoSs do not fit within GW170817s 90\% posterior on EoS - so we expect deviations consistent with the ``unconstrained" set of EoSs, rather than the ``constrained" set.}, while HS/NS combinations disagree significantly.
This can be explained by the large reduction in tidal deformability proceeding the transition pressure for hybrid stars, as shown in Fig.~\ref{fig:hybrid}.
When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, 
the difference between tidal deformabilities becomes larger than expected for pure hadronic-matter stars.
This results in a large deviation in the NS binary Love relations $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality.

@@

To further investigate this phenomena, we consider binary Love fits to the HS or NS branches \emph{individually}.
It was found that the binary Love relations failed to properly fit to the collection of full hybrid star EoSs, due to the varying transitional masses $M_{\text{tr}}$ across the various EoSs.
To compensate for these differences, we separate the two branches into the NS (hadronic matter) and HS (hybrid matter) branches.
We first observe that the NS branches obey the ``hadronic" binary Love relations derived in Sec.~\ref{sec:binLove-nuclear} within the same EoS variability, indicating no further need for additional fits.
However, the HS branches do not follow the same relations, suggesting the need for a new ``hybrid binary love fit" pertaining to this branch alone.
We begin by fitting the binary Love curve in Eq.~\ref{eq:binLovefit} to the HS branches, resulting in the fit coefficients tabulated in the bottom row of Tab.~\ref{tab:binLovefit}.
We note here that the Newtonian limit for this fit is not physical for quark-star matter, which does not reach low enough central densities.
Attempts were made to remedy this by allowing the polytropic index $n$ to be either $0$ or a free fitting parameter, both of which failed.
We instead leave the fits as they are, with the disclaimer that they do not properly limit to the Newtonian case.
The fits are displayed in the top panel of Fig.~\ref{fig:binLove} as dot-dashed blue curves, showing a good relationship with the hybrid star branches used in the analysis.
We urge caution with the use of these fits, as the limited sample size of 10 EoSs results in a less accurate fit than its nuclear-matter counterpart.
Similar to the previous section, the fractional difference from the fit for each HS branch is computed, resulting in a maximum EoS variability of $18.49$\% for $q=0.90$.
This result is strongly consistent with the results found for the nuclear matter fits of Sec.~\ref{sec:binLove-nuclear}.

We conclude this section with the observation that the hybrid star EoSs do \emph{not} conform to the fits performed on nuclear matter EoSs.
This is not surprising, as the hybrid branch of the EoSs forces inconsistent results between $\Lambda_1$ and $\Lambda_2$ with different masses; an issue not present for the single-star I-Love-Q relations.
By separating the two branches of the hybrid EoSs, we find a new ``hybrid" branch binary Love fit which gives consistent results to that found for the nuclear matter fits.

@@

In this section, we investigate the residuals on $\Lambda_a(\Lambda_s,q)$ in order to marginalize over the intrinsic error found in the binary Love EoS-insensitive relations.
In particular, we restrict our focus to only the constrained set of EoSs.
Residuals in $\Lambda_a$ are computed as $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$, where $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the sample EoSs, and $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the value obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binLove-nuclear}.
We follow this up by converting the $\Lambda_a$ residuals into $\lambda_0$, allowing us to approximate the overall systematic errors on $\lambda_0$ from using the improved binary Love relations.

@@

\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{residuals.pdf}
\end{center}
\caption{
Residuals on $\lambda_0$ computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binLove-nuclear} for both constrained and unconstrained sets of EoSs.
These residuals obey Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
These uncertainties correspond roughly to the systematic errors introduced on the parameter extraction of $\lambda_0$ upon the use of binary Love relations.
However, to take into account the systematic errors found in high-error regions of the parameter space, we instead set the systematic error to be the 90th percentile, $P_{90}=13.19$.
Observe that the systematic errors from using the improved (constrained) binary Love relations are negligible compared to the statistical errors accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=170.1$.
}
\label{fig:residuals}
\end{figure}

@@

Future work on this subject entails an investigation into the improvement of alternative EoS insensitive relations, such as the multipole Love relations between various $l$-th order electric, magnetic, and shape tidal deformabilities as discussed in Ref.~\cite{Yagi:Multipole}.
Additionally, Lackey \emph{et al}. presented surrogate models of non-spinning effective-one-body waveform models with the the use of universal relations in Refs.~\cite{Lackey:Surrogate, Lackey:EOB}.
By reducing the number of required waveform model parameters, surrogate models aid in the extraction of NS observables from GW detections.
The improvement in the multipole love relations can then be used to increase the accuracy of surrogate models.

>>>>

\subsection{Binary love relations}\label{sec:binary}
Next we consider improvements to the binary Love relations.
Similar to Sec.~\ref{sec:ilq}, we consider two distinct classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
Following Ref.~\cite{Yagi:binLove}, we begin by fitting the binary Love relations to the constrained and unconstrained sets of EoSs using the two-dimensional curve:
\begin{equation}\label{eq:binLovefit}
\Lambda_a=F_n(q) \frac{1+ \sum_{i=1}^3 \sum_{j=1}^2 b_{ij}q^j x^{i/5}}{1 + \sum_{i=1}^3 \sum_{j=1}^2 c_{ij}q^j x^{i/5}} \Lambda_s^{\alpha}.
\end{equation}
Here, q is the mass ratio $q \equiv m_1/m_2$ with $m_1 \leq m_2$, and $F_n(q)$ is the Newtonian-limiting control factor given by:
\begin{equation}
F_n(q) \equiv \frac{1-q^{10/(3-n)}}{1+q^{10/(3-n)}}.
\end{equation}
The updated fit parameters for the constrained set of EoSs can be found in Table~\ref{tab:binLovefit}.
Notice how, unlike the individual NS I-Love-Q relations, these relations also depend on the ratio of constituent masses in the binary system.
\begin{table*}
\centering
\caption{
Updated fit parameters for the binary Love relations, as given by the curve found in Eq.~\ref{eq:binLovefit}.
}\label{tab:binLovefit}
\addtolength{\tabcolsep}{1pt} 
\begin{tabular}{c  c  c  c  c  c  c  c c c c c c c} 
 \hline
 \hline
$n$ & $\alpha$ & $b_{11}$ & $b_{12}$ & $b_{21}$ & $b_{22}$ & $b_{31}$ & $b_{32}$ & $c_{11}$ & $c_{12}$ & $c_{21}$ & $c_{22}$ & $c_{31}$ & $c_{32}$\\
\hline
$0.743$ & $-1$ & $-14.40$ & $14.45$ & $31.36$ & $-32.25$ & $-22.44$ & $20.35$ & $-15.25$ & $15.37$ & $37.33$ & $-43.20$ & $-29.93$ & $35.18$\\
 \hline
 \hline
\end{tabular}
\addtolength{\tabcolsep}{-1pt}
\end{table*}

Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both the constrained and unconstrained sets of EoSs.
Observe how once again, the constrained set of EoSs show a considerable improvement upon both the unconstrained set of EoSs, as well as the results found in previous works~\cite{Yagi:binLove}.
Additionally, the unconstrained set of EoSs show similar, yet slightly larger EoS variation than was previously found in Ref.~\cite{Yagi:binLove} due to the random sampling taken into account in this analysis.
Once again, the maximum EoS variability (in terms of both absolute and fractional differences from the fit) is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio considered here.

\begin{figure}
\begin{center} 
\includegraphics[width=\linewidth]{binLoveAbsolute.eps}%{binLove.eps}
\end{center}
\caption{
Binary Love relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
In this figure, the top panel displays the EoS-insensitive relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines (note there are 2 fits for each mass ratio, corresponding to the constrained and unconstrained sets of EoSs), while the bottom 3 panels correspond to the absolute EoS variation for each mass ratio.
Observe how the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
The maximal EoS variability (shown as a the fractional difference for comparison purposes) for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
Additionally shown are the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves).
Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
}
\label{fig:binLove}
\end{figure}

Additionally shown in Fig.~\ref{fig:binLove} are the binary Love relations for the 10 hybrid EoSs discussed in previous sections.
As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote these as ``HS"), and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote these as ``NS").
Contrary to the single-star relations (I-Love-Q, C-Love, and R-Love) where the hybrid stars moderately agree with their nuclear matter counterparts, the binary-star relations show large disagreement, which can be seen in Fig.~\ref{fig:binLove}.
Observe how the agreement with the fit is quite good at low pressures (large $\Lambda_s$) where the the binaries consist of NS/NS combinations (here, both stars' EoSs consist of the same class of nuclear matter as the constrained EoSs).
Once the critical pressure is reached, one or both stars transition into the hybrid branches, resulting in large reductions in tidal deformability as shown in Fig.~\ref{fig:hybridML}.
When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, 
the difference between tidal deformabilities becomes larger than expected for pure hadronic-matter stars.
This results in a large deviation in the sums and differences of tidal deformabilities $(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality and generating the large ``bump" in the binary love relations for hybrid stars\footnote{This discrepancy is not present in the I-Love-Q and C-Love relations due to their singular nature.} seen in Fig~\ref{fig:binLove}.

Due to the inconsistencies in the sums and differences of tidal deformabilities for binary hybrid star systems, we conclude that hybrid stars do \emph{not} agree with the traditional nuclear matter binary Love relations.
A number of attempts were made to reconcile these differences, such as performing separate ``HS" binary Love relations fitted directly to the hybrid star branches of the EoSs.
This analysis quickly left the scope of the paper due to the large number of parameters required to control the varying transitional pressures through different EoSs.
Therefore, we leave this analysis on the hybrid star binary Love relations to be discussed in future works.
There, we anticipate generating large numbers of hybrid star EoSs with varying transition masses to be taken into account as an additional fitting parameter in a piece-wise fitting function designed to take into account the ``bumps" in the binary Love relations.

\iffalse%%%%%%%%%%%%%%%%%%% COMMENTED OUT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Hybrid quark-hadron stars}\label{sec:binLove-hybrid}
As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
We consider 3 classes of binary systems in this analysis:
\begin{itemize}
\item HS/NS binary: consists of one massive hybrid star, and one small hadronic neutron star,
\item NS/NS binary: consists of two small-mass hadronic neutron stars,
\item HS/HS binary: consists of two massive hybrid stars.
\end{itemize}

To determine how each of class of binary NS systems obey our improved binary Love relations, we pick a representative set of 10 binary pairs from each class from the ACB5 hybrid EoS, with a transition at $M_{\text{tr}} \approx 1.4 \text{ M}_{\odot}$.
Binary Love values are computed for each pair, and fractional residuals from the binary Love curve found in Sec.~\ref{sec:binary} are determined and compared to the values from the constrained set of EoSs.
The results are shown in Fig.~\ref{fig:hybrid}.
First, we note that the NS/NS combination of stars gives consistent results to that found earlier -- as expected.
Next, we observe that HS/HS combinations agree moderately with previous relations\footnote{Note that these EoSs do not fit within GW170817s 90\% posterior on EoS - so we expect deviations consistent with the ``unconstrained" set of EoSs, rather than the ``constrained" set.}, while HS/NS combinations disagree significantly.
This can be explained by the large reduction in tidal deformability proceeding the transition pressure for hybrid stars, as shown in Fig.~\ref{fig:hybrid}.
When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, 
the difference between tidal deformabilities becomes larger than expected for pure hadronic-matter stars.
This results in a large deviation in the NS binary Love relations $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality.

@@

To further investigate this phenomena, we consider binary Love fits to the HS or NS branches \emph{individually}.
It was found that the binary Love relations failed to properly fit to the collection of full hybrid star EoSs, due to the varying transitional masses $M_{\text{tr}}$ across the various EoSs.
To compensate for these differences, we separate the two branches into the NS (hadronic matter) and HS (hybrid matter) branches.
We first observe that the NS branches obey the ``hadronic" binary Love relations derived in Sec.~\ref{sec:binary} within the same EoS variability, indicating no further need for additional fits.
However, the HS branches do not follow the same relations, suggesting the need for a new ``hybrid binary love fit" pertaining to this branch alone.
We begin by fitting the binary Love curve in Eq.~\ref{eq:binLovefit} to the HS branches, resulting in the fit coefficients tabulated in the bottom row of Tab.~\ref{tab:binLovefit}.
We note here that the Newtonian limit for this fit is not physical for quark-star matter, which does not reach low enough central densities.
Attempts were made to remedy this by allowing the polytropic index $n$ to be either $0$ or a free fitting parameter, both of which failed.
We instead leave the fits as they are, with the disclaimer that they do not properly limit to the Newtonian case.
The fits are displayed in the top panel of Fig.~\ref{fig:binLove} as dot-dashed blue curves, showing a good relationship with the hybrid star branches used in the analysis.
We urge caution with the use of these fits, as the limited sample size of 10 EoSs results in a less accurate fit than its nuclear-matter counterpart.
Similar to the previous section, the fractional difference from the fit for each HS branch is computed, resulting in a maximum EoS variability of $18.49$\% for $q=0.90$.
This result is strongly consistent with the results found for the nuclear matter fits of Sec.~\ref{sec:binary}.

We conclude this section with the observation that the hybrid star EoSs do \emph{not} conform to the fits performed on nuclear matter EoSs.
This is not surprising, as the hybrid branch of the EoSs forces inconsistent results between $\Lambda_1$ and $\Lambda_2$ with different masses; an issue not present for the single-star I-Love-Q relations.
By separating the two branches of the hybrid EoSs, we find a new ``hybrid" branch binary Love fit which gives consistent results to that found for the nuclear matter fits. 
\fi%%%%%%%%%%%%%%%%%%% COMMENTED OUT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this section, we investigate the residuals on $\Lambda_a(\Lambda_s,q)$ in order to marginalize over the intrinsic error found in the binary Love EoS-insensitive relations.
In particular, we restrict our focus to only the constrained set of EoSs.
Residuals in $\Lambda_a$ are computed as $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$, where $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the sample EoSs, and $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the value obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binary}.
We follow this up by converting the $\Lambda_a$ residuals into $\lambda_0$, allowing us to approximate the overall systematic errors on $\lambda_0$ from using the improved binary Love relations.

@@

\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{residuals.pdf}
\end{center}
\caption{
Residuals on $\lambda_0$ computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binary} for both constrained and unconstrained sets of EoSs.
These residuals obey Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
These uncertainties correspond roughly to the systematic errors introduced on the parameter extraction of $\lambda_0$ upon the use of binary Love relations.
However, to take into account the systematic errors found in high-error regions of the parameter space, we instead set the systematic error to be the 90th percentile, $P_{90}=13.19$.
Observe that the systematic errors from using the improved (constrained) binary Love relations are negligible compared to the statistical errors accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=170.1$.
}
\label{fig:residuals}
\end{figure}

@@

Future work on this subject entails an investigation into the improvement of alternative EoS insensitive relations, such as the multipole Love relations between various $l$-th order electric, magnetic, and shape tidal deformabilities as discussed in Ref.~\cite{Yagi:Multipole}.
Additionally, Lackey \emph{et al}. presented surrogate models of non-spinning effective-one-body waveform models with the the use of universal relations in Refs.~\cite{Lackey:Surrogate, Lackey:EOB}.
By reducing the number of required waveform model parameters, surrogate models aid in the extraction of NS observables from GW detections.
The improvement in the multipole love relations can then be used to increase the accuracy of surrogate models.
Additionally, we plan on a more comprehensive analysis into the intricacies of new hybrid star binary Love relations, as discussed in Sec.~\ref{sec:binary}.
